Foreground Detection via Deep Variation Transformation

### 2018-12-16 draft.tex
revised to the first paragraph of Network architecture

\subsection*{Training Data Generation}
% 第一步是对原视频进行采样
%从描述事实开始
Fundamentally, 
background subtraction is a classification of pixels' observations in time sequence.
% 我们的动机
In this work,
the deep learning network is utilized to learn the pattern of variations implied in the observations of pixels.
% 基于这个动机，我们是怎么做的
Therefore,
the training data feed into network is one kinds of description of pixels' variation,
which is actually patches consist of pixels' observations.
%
In contrast, the output of the network is the probability of corresponding pixels belong to foreground or background,
and the network is devised with an end-to-end architecture to transform the intensity of pixels to the probability of category the pixels belong to.

@@

\subsection*{Network Work Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $x \in \mathcal{X}$ 
to the probability of the corresponding pixel belong to foreground or background.

As shown in the \reffig{flow_chart},
a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels.
%
The input of network is the training patches $S(m,n)$ extracted from different pixels
and the output of network is the labeled patches captured from Groundtruth frames.
%
The training procedure is the transformation from the training patches to the labelling patches,
which is shown as follows:
% 
% the architecture of network 
% 
% Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
% Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
% However, the size of feature maps will shrink quickly during forward computation. 
% In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
% After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
% The transformed pixel patch is defined as:
\begin{equation}
    \begin{split}
        S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
    \end{split}
\end{equation}
where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
Another advantage of symmetric padding is that the order information still remains.

@@

>>>>

\subsection*{Training Data Generation}
% 第一步是对原视频进行采样
%从描述事实开始
Fundamentally, 
background subtraction is a classification of pixels' observations in time sequence.
% 我们的动机
In this work,
the deep learning network is utilized to learn the pattern of variations implied in the observations of pixels.
% 基于这个动机，我们是怎么做的
Therefore,
the training data feed into network is one kinds of description of pixels' variation,
which is actually patches consist of pixels' temporal observations.
%
In contrast, the output of the network is the probability of corresponding pixels belong to foreground or background,
and the network is devised with an end-to-end architecture to transform the intensity of pixels to the probability of category the pixels belong to.

@@

\subsection*{Network Work Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
to the probability $p \in \mathcal{P}$ of the corresponding pixel belong to foreground or background,
and a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels as shown in the \reffig{flow_chart}.
%
Mathematically, the training procedure is shown as follows:
\begin{equation}
    \begin{split}
        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
    \end{split}
\end{equation}
where $\mathcal{P}(x,y)$ is denoted as the probability, $\mathcal{S}(m,n)$ is the input patch of network and $f_{\theta_i}$ is represents different layers of network.
% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
% Another advantage of symmetric padding is that the order information still remains.

@@

The network used in this work is devised as an end-to-end architecture,

% 
% 
% As shown in the \reffig{flow_chart},
% %
% The input of network is the training patches $S(m,n)$ extracted from different pixels
% and the output of network is the labeled patches captured from Groundtruth frames.
% %
% The training procedure is the transformation from the training patches to the labelling patches,
% which is shown as follows:
% % 
% % the architecture of network 
% % 
% % Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
% % Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
% % However, the size of feature maps will shrink quickly during forward computation. 
% % In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
% % After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
% % The transformed pixel patch is defined as:
% \begin{equation}
%     \begin{split}
%         S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
%           & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
%     \end{split}
% \end{equation}
